Tropical Mathematics and the Lambda Calculus

### 2023-01-23 appIII.tex
Commit serale

\subsubsection{The language $\BSTLC$}
In Section 4 we considered a variant $\BSTLC$ of $\STLC$ with linear simple types and a graded exponential $!_{n}A$, for all $n\in \BB N$, corresponding to a somehow simplified version of the language $\mathrm{Fuzz}$ \cite{Reed2010}. 
%The terms are generated by the grammar:
%
%{
%\begin{minipage}{\textwidth}
%\begin{align*}
%M:= x\mid \lambda x.M\mid MM \mid !M \mid \mathsf{let}\  !x=M \ \mathsf{in}\  M%\mid (t,u)\mid  \mathsf{let}\  (x,y)=t \ \mathsf{in} \  u 
%\end{align*}\end{minipage}}\medskip\\
%For the purposes of this article we limited ourselves to a minimal fragment of this language. For a more practical language see \cite{Reed2010,Gaboardi2017}.

@@

\subsubsection{$(\LREL, !_{n})$ is a model of $\BSTLC$}

>>>>

\subsection{Section~\ref{sec:3B}: the language $\BSTLC$}

In Section 4 we considered a variant $\BSTLC$ of $\STLC$ with linear simple types and a graded exponential $!_{n}A$, for all $n\in \BB N$, corresponding to a somehow simplified version of the language $\mathrm{Fuzz}$ \cite{Reed2010}. 
%The terms are generated by the grammar:
%
%{
%\begin{minipage}{\textwidth}
%\begin{align*}
%M:= x\mid \lambda x.M\mid MM \mid !M \mid \mathsf{let}\  !x=M \ \mathsf{in}\  M%\mid (t,u)\mid  \mathsf{let}\  (x,y)=t \ \mathsf{in} \  u 
%\end{align*}\end{minipage}}\medskip\\
%For the purposes of this article we limited ourselves to a minimal fragment of this language. For a more practical language see \cite{Reed2010,Gaboardi2017}.

@@

\subsection{Proofs from Section~\ref{sec:3B}: $(\LREL, !_{n})$ is a model of $\BSTLC$}

### 2023-01-23 appIV.tex
Commit serale

\subsubsection{Proof of Theorem~\ref{thm:LREL!CCDC}}

@@

%\paragraph{Taylor Expansion }
\subsubsection{Taylor Expansion in $\LREL_!$}

To check the validity of Taylor expansion in $\LREL_!$ we must further check the following equation, given $f\in \LREL_!(C, B^{A})$ and $g\in \LREL_!(C,A)$:
$$
\mathsf{ev}\circ \langle f,g\rangle= \inf_{n\in \BB N}
\left\{(( \cdots (\Lambda^{-}(f) \underbrace{\star g)\cdots )\star g}_{n\text{ times}})\circ \langle \mathrm{id}, \infty\rangle\right\}
$$
where:
\begin{enumerate}
\item $\mathsf{ev}\in \LREL_!(B^{A}+A, B)$ is the canonical \emph{evaluation} morphism;

@@

Let us first compute the three morphisms $\mathsf{ev}, \Lambda^{-}$ and $\star$ explicitly:
\begin{enumerate}

\item $\mathsf{ev}\in \Lawv^{ \C M_{\mathsf{fin}}(  ( \C M_{\mathsf{fin}}(A)\times B)       +  A    ) \times B  }$ is given by
$$\mathsf{ev}_{\mu,y}=
 \begin{cases}
 0 & \text{ if } \mu=[ \langle\rho, y\rangle]  \oplus \rho \\
 \infty & \text{ otherwise}
 \end{cases}
 $$
and observe that, given $f\in \LREL_!(C, B^{A})$ and $g\in \LREL_!(C,A)$, 
$$
\big(\mathsf{ev}\circ \langle f,g\rangle \big)_{\chi, y}= 
\inf\Big \{ 
\sum_{i=1}^{m}g_{\chi_{i},x_{i}}+
f_{\chi', \langle [x_{1},\dots, x_{m}],y\rangle}
\mid 
x_{1},\dots, x_{m}\in A,
\chi= \chi'+\sum_{i=1}^{m}\chi_{i}, 
\Big \}
$$

\item given $g\in \LREL_!(C, B^{A})$, 
$\Lambda^{-}(g)\in \LREL_!(C+A, B)$ is given by 
$$
\big(\Lambda^{-}(g)\big)_{\rho\oplus\mu,y}=g_{\rho, \langle \mu,y\rangle}
$$

\item $f\star g$ is given by 
$$
(f\star g)_{\rho\oplus\mu,y}=
\inf\Big\{
g_{\rho',x}+
f_{\rho''\oplus(\mu+x)}
\mid
x\in A,
\rho= \rho'+\rho''
\Big\}
$$

Given the definition of $\mathsf{ev}\circ \langle f,g\rangle$, to check the Taylor equation it is enough to check that, for all $N\in \BB N$, 
$$
\left((( \cdots (\Lambda^{-}(f) \underbrace{\star g)\cdots )\star g}_{N\text{ times}})\circ \langle \mathrm{id}, \infty\rangle\right)_{\chi,y}=
\inf\Big \{ 
\sum_{i=1}^{N}g_{\chi_{i},x_{i}}+
f_{\chi', \langle [x_{1},\dots, x_{N}],y\rangle}
\mid 
\begin{matrix}
x_{1},\dots, x_{N}\in A,\\
\chi= \chi'+\sum_{i=1}^{N}\chi_{i}
\end{matrix}
\Big \}
$$

@@

\item otherwise, let $F=(( \cdots (\Lambda^{-}(f) \underbrace{\star g)\cdots )\star g}_{N-1\text{ times}})$, so that by I.H.~we have
$$
F_{\chi\oplus\mu,y}=
\inf\Big \{ 
\sum_{i=1}^{N-1}g_{\chi_{i},x_{i}}+
f_{\chi', \langle\mu+ [x_{1},\dots, x_{N-1}],y\rangle}
\mid 
\begin{matrix}
x_{1},\dots, x_{N-1}\in A,\\
\chi= \chi'+\sum_{i=1}^{N-1}\chi_{i}
\end{matrix}
\Big \}
$$
Then we have
{\small
\begin{align*}
\big( F\star g\big)_{\chi\oplus\mu,y}
&=
\inf \left \{
g_{\chi',x}+F_{\chi''\oplus(\mu+x)}
\mid
x\in A, \chi=\chi'+\chi''
\right\}\\
&=
\inf\left \{ 
g_{\chi',x}+
\inf\left\{
\sum_{i=1}^{N-1}g_{\chi_{i},x_{i}}+
f_{\chi'', \langle\mu+ [x_{1},\dots, x_{N-1}]+x,y\rangle}
\mid 
\begin{matrix}
x_{1},\dots, x_{N-1}\in A,\\
\chi^{*}= \chi''+\sum_{i=1}^{N-1}\chi_{i}
\end{matrix}
\right\}
\ 
\Big\vert \ 
\begin{matrix}
x\in A,\\
\chi=\chi'+\chi^{*}
\end{matrix}
\right \}\\
&=
\inf\Big \{ 
g_{\chi',x}+
\sum_{i=1}^{N-1}g_{\chi_{i},x_{i}}+
f_{\chi'', \langle\mu+ [x_{1},\dots, x_{N-1}]+x,y\rangle}
\mid 
\begin{matrix}
x,x_{1},\dots, x_{N-1}\in A,\\
\chi= \chi'+\chi''+\sum_{i=1}^{N-1}\chi_{i}
\end{matrix}
\Big \}\\
&=
\inf\Big \{ 
\sum_{i=1}^{N}g_{\chi_{i},x_{i}}+
f_{\chi', \langle\mu+ [x_{1},\dots, x_{N}],y\rangle}
\mid 
\begin{matrix}
x_{1},\dots, x_{N}\in A,\\
\chi= \chi'+\sum_{i=1}^{N}\chi_{i}
\end{matrix}
\Big \}.
\end{align*}
}
\end{itemize}

\subsubsection{The language and the semantics of the $\STDLC$}\label{secApp:STDLC}

The language we mainly consider in the main paper is the differential $\lambda$-calculus $\STDLC$, that we briefly define here, following [Section 3, \cite{Manzo2010}].

The terms and the sums\footnote{Usually what we call here ``terms'' are called ``simple terms'', and what we call here ``sums'' are called ``differential terms''.} are mutually generated by the following grammars:

@@

One lifts as usual the interpretation to types and contexts as $\model{A\to B}:=\model A\to \model B$ and $\model{x_1:A_1,\dots,x_n:A_n}:=\Pi_{i=1}^n\model{x_i:A_i}$.

Then, one inductively defines an interpretation $\model{\Gamma \vdash M:A}\in\C C(\model \Gamma,\model A)$ of $\Gamma \vdash M:A$ and one of $\model{\Gamma \vdash \BB T:A}\in\C C(\model \Gamma,\model{A})$ of $\Gamma \vdash \BB T:A$ by induction as:
\begin{itemize}
 \item $\model{\Gamma, x:A \vdash x:A}:=\pi_2$
 \item $\model{\Gamma, x:A \vdash y:B}:=\model{\Gamma \vdash y:B}\circ \pi_1\quad\textit{ if } y\neq x$
 \item $\model{\Gamma\vdash \lambda x.M:A\to B}:=\Lambda(\model{\Gamma,x:A\vdash M:B})$
 \item $\model{\Gamma \vdash M\BB T:B}:=\mathsf{ev} \circ \langle \, \model{\Gamma \vdash M:A\to B}, \model{\Gamma \vdash \BB T:A} \, \rangle$
 \item $\model{\Gamma \vdash \Der [M] \cdot N:A\to B}:=\Lambda\left(\Lambda^-(\model{\Gamma \vdash M:A\to B})\star \model{\Gamma \vdash N:A}\right)$
 \item $\model{\Gamma \vdash 0:A}:=:0 \qquad \textit{(the $0$ element of $\C C(\model \Gamma,\model A)$)}$
 \item $\model{\Gamma \vdash M+\BB T:A}:=\model{\Gamma \vdash M:A}+\model{\Gamma \vdash \BB T:A}$ \qquad \textit{(the $+$ operation on $\C C(\model \Gamma,\model A)$)}
\end{itemize}
\end{definition}

@@

In the main paper we write $\model M$, but of course we mean $\model{\Gamma \vdash M:A}$.

\subsubsection{The Taylor expansion of the $\STLC$}

In the last lines of Section~\ref{sec:3B} we state Corollary~\ref{cor:T(M)=M} which is about the Taylor expansion of a ordinary $\lambda$-terms $M$.
In the main paper we do not define it, let us briefly recall it here.
For details, the reader can look at the many papers on the subject pointed in the bibliography.

>>>>

\subsection{Section~\ref{sec:3C}: Proof of Theorem~\ref{thm:LREL!CCDC}}

@@

%\paragraph{Taylor Expansion }
\subsection{Section~\ref{sec:3C}: proof of  Theorem~\ref{thm:modelsTaylor}}

Theorem~\ref{thm:modelsTaylor} states the validity of Taylor expansion in $\LREL_!$.

We must check for it the following equation, given $f\in \LREL_!(C, B^{A})$ and $g\in \LREL_!(C,A)$:
$$
\mathsf{ev}\circ \langle f,g\rangle= \inf_{n\in \BB N}
\left\{(( \cdots (\Lambda^{-}(f) \underbrace{\star g)\cdots )\star g}_{n\text{ times}})\circ \langle \mathrm{id}, \infty\rangle\right\}
$$
where:
\begin{enumerate}
\item $\mathsf{ev}\in \LREL_!(B^{A}+A, B)$ is the canonical \emph{evaluation} morphism;

@@

We do it in the following $4$ steps.

\begin{enumerate}

\item Let us compute the morphism $\mathsf{ev}$ explicitly: $\mathsf{ev}\in \Lawv^{ \C M_{\mathsf{fin}}(  ( \C M_{\mathsf{fin}}(A)\times B)       +  A    ) \times B  }$ is given by
$$\mathsf{ev}_{\mu,y}=
 \begin{cases}
 0 & \text{ if } \mu=[ \langle\rho, y\rangle]  \oplus \rho \\
 \infty & \text{ otherwise}
 \end{cases}
 $$
and observe that, given $f\in \LREL_!(C, B^{A})$ and $g\in \LREL_!(C,A)$, 
$$
\big(\mathsf{ev}\circ \langle f,g\rangle \big)_{\chi, y}= 
\inf\Big \{ 
\sum_{i=1}^{m}g_{\chi_{i},x_{i}}+
f_{\chi', \langle [x_{1},\dots, x_{m}],y\rangle}
\mid 
x_{1},\dots, x_{m}\in A,
\chi= \chi'+\sum_{i=1}^{m}\chi_{i}, 
\Big \}
$$

\item Let us compute the morphism $\Lambda^{-}$ explicitly: given $g\in \LREL_!(C, B^{A})$, 
$\Lambda^{-}(g)\in \LREL_!(C+A, B)$ is given by 
$$
\big(\Lambda^{-}(g)\big)_{\rho\oplus\mu,y}=g_{\rho, \langle \mu,y\rangle}
$$

\item Let us compute the morphism $\star$ explicitly: $f\star g$ is given by 
$$
(f\star g)_{\rho\oplus\mu,y}=
\inf\Big\{
g_{\rho',x}+
f_{\rho''\oplus(\mu+x)}
\mid
x\in A,
\rho= \rho'+\rho''
\Big\}
$$

\item We can now conclude: given the definition of $\mathsf{ev}\circ \langle f,g\rangle$, to check the Taylor equation it is enough to check that, for all $N\in \BB N$, 
$$
\left((( \cdots (\Lambda^{-}(f) \underbrace{\star g)\cdots )\star g}_{N\text{ times}})\circ \langle \mathrm{id}, \infty\rangle\right)_{\chi,y}=
\inf\Big \{ 
\sum_{i=1}^{N}g_{\chi_{i},x_{i}}+
f_{\chi', \langle [x_{1},\dots, x_{N}],y\rangle}
\mid 
\begin{matrix}
x_{1},\dots, x_{N}\in A,\\
\chi= \chi'+\sum_{i=1}^{N}\chi_{i}
\end{matrix}
\Big \}
$$

@@

\item otherwise, let $F=(( \cdots (\Lambda^{-}(f) \underbrace{\star g)\cdots )\star g}_{N-1\text{ times}})$, so that by I.H.~we have
$$
F_{\chi\oplus\mu,y}=
\inf\Big \{ 
\sum_{i=1}^{N-1}g_{\chi_{i},x_{i}}+
f_{\chi', \langle\mu+ [x_{1},\dots, x_{N-1}],y\rangle}
\mid 
\begin{matrix}
x_{1},\dots, x_{N-1}\in A,\\
\chi= \chi'+\sum_{i=1}^{N-1}\chi_{i}
\end{matrix}
\Big \}
$$
Then we have
{\small
\begin{align*}
\big( F\star g\big)_{\chi\oplus\mu,y}
&=
\inf \left \{
g_{\chi',x}+F_{\chi''\oplus(\mu+x)}
\mid
x\in A, \chi=\chi'+\chi''
\right\}\\
&=
\inf\left \{ 
g_{\chi',x}+
\inf\left\{
\sum_{i=1}^{N-1}g_{\chi_{i},x_{i}}+
f_{\chi'', \langle\mu+ [x_{1},\dots, x_{N-1}]+x,y\rangle}
\mid 
\begin{matrix}
x_{1},\dots, x_{N-1}\in A,\\
\chi^{*}= \chi''+\sum_{i=1}^{N-1}\chi_{i}
\end{matrix}
\right\}
\ 
\Big\vert \ 
\begin{matrix}
x\in A,\\
\chi=\chi'+\chi^{*}
\end{matrix}
\right \}\\
&=
\inf\Big \{ 
g_{\chi',x}+
\sum_{i=1}^{N-1}g_{\chi_{i},x_{i}}+
f_{\chi'', \langle\mu+ [x_{1},\dots, x_{N-1}]+x,y\rangle}
\mid 
\begin{matrix}
x,x_{1},\dots, x_{N-1}\in A,\\
\chi= \chi'+\chi''+\sum_{i=1}^{N-1}\chi_{i}
\end{matrix}
\Big \}\\
&=
\inf\Big \{ 
\sum_{i=1}^{N}g_{\chi_{i},x_{i}}+
f_{\chi', \langle\mu+ [x_{1},\dots, x_{N}],y\rangle}
\mid 
\begin{matrix}
x_{1},\dots, x_{N}\in A,\\
\chi= \chi'+\sum_{i=1}^{N}\chi_{i}
\end{matrix}
\Big \}.
\end{align*}
}
\end{itemize}
\end{enumerate}

\subsection{Section~\ref{sec:3C}: The language and the semantics of the $\STDLC$}\label{secApp:STDLC}

The language we mainly consider in the paper is the differential $\lambda$-calculus $\STDLC$, that we briefly define here, following [Section 3, \cite{Manzo2010}].

The \emph{terms} and the \emph{sums}\footnote{Usually what we call here ``terms'' are called ``simple terms'', and what we call here ``sums'' are called ``differential terms''.} are mutually generated by the following grammars:

@@

One lifts as usual the interpretation to types and contexts as $\model{A\to B}:=\model A\to \model B$ (the exponential object in $\C C$) and $\model{x_1:A_1,\dots,x_n:A_n}:=\Pi_{i=1}^n\model{x_i:A_i}$.

One inductively defines an interpretation $\model{\Gamma \vdash \BB T:A}\in\C C(\model \Gamma,\model{A})$ of $\Gamma \vdash \BB T:A$ by induction as:
\begin{itemize}
 \item $\model{\Gamma, x:A \vdash x:A}:=\pi_2$
 \item $\model{\Gamma, x:A \vdash y:B}:=\model{\Gamma \vdash y:B}\circ \pi_1\quad\textit{ if } y\neq x$
 \item $\model{\Gamma\vdash \lambda x.M:A\to B}:=\Lambda(\model{\Gamma,x:A\vdash M:B})$
 \item $\model{\Gamma \vdash M\BB T:B}:=\mathsf{ev} \circ \langle \, \model{\Gamma \vdash M:A\to B}, \model{\Gamma \vdash \BB T:A} \, \rangle$
 \item $\model{\Gamma \vdash \Der [M] \cdot N:A\to B}:=\Lambda\left(\Lambda^-(\model{\Gamma \vdash M:A\to B})\star \model{\Gamma \vdash N:A}\right)$
 \item $\model{\Gamma \vdash 0:A}:=:0 \qquad \textit{(the $0$ element of $\C C(\model \Gamma,\model A)$)}$
 \item $\model{\Gamma \vdash M+\BB T:A}:=\model{\Gamma \vdash M:A}+\model{\Gamma \vdash \BB T:A}$ \qquad \textit{(the $+$ operation on $\C C(\model \Gamma,\model A)$)}
\end{itemize}
\end{definition}

@@

In the paper we write $\model M$, but of course we mean $\model{\Gamma \vdash M:A}$.

\subsection{Section~\ref{sec:3C}: proof of Corollary~\ref{cor:T(M)=M}}

In the last lines of Section~\ref{sec:3B} we state Corollary~\ref{cor:T(M)=M} which is about the Taylor expansion of a ordinary $\lambda$-terms $M$.
In the main paper we do not define it, let us briefly recall it here, and the we prove the Corollary.
For details, the reader can look at the many papers on the subject pointed in the bibliography.

### 2023-01-23 appV.tex
commit
Commit serale

\subsubsection{Concavity}

@@

\subsubsection{Proof of Theorem~\ref{theorem:fepsilon}}

@@

\subsubsection{Continuity of tLs}

We prove here the two results Theorem~\ref{thm:ScottCont} and Theorem~\ref{thm:cont} from Section~\ref{subsec:cont}.

In order to prove Theorem~\ref{thm:cont}, we place ourselves in the general setting of locally convex topological vector spaces (LCTVS), and prove a general result about convex functions in this setting, adapting the argument from [Theorem , \cite{}].

@@

@@

In [Selinger] cones are required to also have ``strict addition'', meaning that $x+y=0 \Rightarrow x=y=0$.
We do not add this requirement since it will automatic hold when considering normed cones.

@@

In [Ehrhard-Pagani-Tasson, Crubillie] a normed $\overline{\R}_{\geq 0}$-cone is simply called a cone.

@@

The fundamental result in order to prove Theorem~\ref{thm:ScottCont} is the following, taken from [Selinger].

@@

\begin{proposition}
 All tropical functions $f:\overline{\R}^X_{\geq 0}\to\overline{\R}^Y_{\geq 0}$ are Scott-continuous on $\R^X_{> 0}$ w.r.t.\ the cone-orders on its domain and codomain.
\end{proposition}
\begin{proof}
 Let $(x_i)_i$ a directed net in $\R^X_{> 0}$ s.t.\ $\bigvee\limits_i x^i$ exists in $\R^X_{> 0}$.
 Then $\inf\limits_i \supnorm{\bigvee\limits_i x^i - x^i} =0$, where $\bigvee\limits_i x^i - x^i$ exists because $\bigvee\limits_i x^i \geq x^i$ for all $i$.
 Since $f$ is $\supnorm{.}$-continuous on $\R^X_{> 0}$ (Corollary \ref{cor:tropCont}), then $\inf\limits_i \supnorm{f(\bigvee\limits_i x^i) - f(x^i)} =0$, where $f(\bigvee\limits_i x^i) - f(x^i)$ exists because $f(\bigvee\limits_i x^i) \geq f(x^i)$ for all $i$ being $f$ monotone (Remark \ref{rmk:tropMonot}).
 We can therefore apply Proposition \ref{prop:infsup} to the directed net $(f(x^i))_i$ in $\overline{\R}^Y_{\geq 0}$, obtaining that $\bigvee\limits_i f(x^i)$ exists in $\overline{\R}^Y_{\geq 0}$ and it coincides with $f(\bigvee\limits_i x^i)$.
\end{proof}

@@

\newpage

@@

The second characterization relates distances with the Taylor expansion. Let us briefly discuss the latter, first.
For all $f: Q\langle X\rangle \to Q\langle Y\rangle$, let $\delta^{(n)}f:Q\langle X^{n}\rangle \to Q\langle Y\rangle$ indicate the $n$-linear function given by 
$$
\delta^{(n)}f( x ^{n})=\mathsf D^{(n)}f( x ^{n}, \infty)
$$

Notice that $\widehat{\delta^{(n)}f}\in Q^{X^{n}\times Y}$ satisfies 
$\widehat{\delta^{(n)}f}_{a_{1},\dots, a_{n},b}= \widehat f_{[a_{1},\dots, a_{n}],b}$.
In other words, $\delta^{(n)}f$ precisely captures the behavior of $f$ when applied to multisets of length $n$. Moreover, the full behavior of $f$ can be recovered from the functions $\delta^{(n)}f$ using the Taylor expansion which, in its tropical form, reads as:
\begin{equation*}
f( x )= \inf_{n}\left \{\mathsf D^{(n)}f( x ^{n},\infty)\right\}= \inf_{n}\left \{\delta^{(n)}f( x ^{n})\right\}
%\tag{Tropical Taylor}
\end{equation*}

>>>>

\subsection{Section~\ref{sec:4A}: Proof of Proposition~\ref{prop:nondecr+conc}}

We just show the concavity, the rest being easy.

@@

\subsection{Section~\ref{sec:4A}: Proof of Theorem~\ref{theorem:fepsilon}}

@@

\subsection{Section~\ref{subsec:cont}: proof of Theorem~\ref{thm:cont}}

In order to prove Theorem~\ref{thm:cont}, we place ourselves in the general setting of locally convex topological vector spaces (LCTVS), and prove a general result about convex functions in this setting, adapting, in the main Proposition~\ref{prop:mainLCTVS}, an argument taken from [Proposition 4.4, \cite{Cobzas2017}].

@@

%\newpage
\subsection{Section~\ref{subsec:cont}: proof of Theorem~\ref{thm:ScottCont}}

In order to prove such result we must quickly recall the theory of normed cones, which we do below.

Here we denote with $\overline{\R}_{\geq 0}$ the set $\R_{\geq 0}\cup\set{\infty}$ (the same as $\Lawv$, but we prefer to explicit it here).

\subsubsection{Normed cones}

@@

In \cite{Selinger2004} cones are required to also have ``strict addition'', meaning that $x+y=0 \Rightarrow x=y=0$.
We do not add this requirement since it will automatic hold when considering normed cones.

@@

In, e.g.~\cite{EhrPagTas2018}, a normed $\overline{\R}_{\geq 0}$-cone is simply called a cone.

@@

The fundamental result in order to prove Theorem~\ref{thm:ScottCont} is the following, taken from \cite{Selinger2004}.

@@

We finally obtain the desired:

\begin{theorem}[Theorem~\ref{thm:ScottCont}]
 All tropical functions $f:\overline{\R}^X_{\geq 0}\to\overline{\R}^Y_{\geq 0}$ are Scott-continuous on $\R^X_{> 0}$ w.r.t.\ the cone-orders on its domain and codomain.
\end{theorem}
\begin{proof}
 Let $(x_i)_i$ a directed net in $\R^X_{> 0}$ s.t.\ $\bigvee\limits_i x^i$ exists in $\R^X_{> 0}$.
 Then $\inf\limits_i \supnorm{\bigvee\limits_i x^i - x^i} =0$, where $\bigvee\limits_i x^i - x^i$ exists because $\bigvee\limits_i x^i \geq x^i$ for all $i$.
 Since $f$ is $\supnorm{.}$-continuous on $\R^X_{> 0}$, then $\inf\limits_i \supnorm{f(\bigvee\limits_i x^i) - f(x^i)} =0$, where $f(\bigvee\limits_i x^i) - f(x^i)$ exists because $f(\bigvee\limits_i x^i) \geq f(x^i)$ for all $i$ being $f$ monotone (Remark \ref{rmk:tropMonot}).
 We can therefore apply Proposition \ref{prop:infsup} to the directed net $(f(x^i))_i$ in $\overline{\R}^Y_{\geq 0}$, obtaining that $\bigvee\limits_i f(x^i)$ exists in $\overline{\R}^Y_{\geq 0}$ and it coincides with $f(\bigvee\limits_i x^i)$.
\end{proof}

@@

\subsection{Proofs from Section~\ref{sec:4C}}

@@

The second characterization relates distances with the Taylor expansion. Let us briefly discuss the latter, first.
For all $f: Q\langle X\rangle \to Q\langle Y\rangle$, let $\delta^{(n)}f:Q\langle X^{n}\rangle \to Q\langle Y\rangle$ indicate the $n$-linear function given by 
$$
\delta^{(n)}f( x ^{n})= D^{(n)}f( x ^{n}, \infty)
$$

Notice that $\widehat{\delta^{(n)}f}\in Q^{X^{n}\times Y}$ satisfies 
$\widehat{\delta^{(n)}f}_{a_{1},\dots, a_{n},b}= \widehat f_{[a_{1},\dots, a_{n}],b}$.
In other words, $\delta^{(n)}f$ precisely captures the behavior of $f$ when applied to multisets of length $n$. Moreover, the full behavior of $f$ can be recovered from the functions $\delta^{(n)}f$ using the Taylor expansion which, in its tropical form, reads as:
\begin{equation*}
f( x )= \inf_{n}\left \{ D^{(n)}f( x ^{n},\infty)\right\}= \inf_{n}\left \{\delta^{(n)}f( x ^{n})\right\}
%\tag{Tropical Taylor}
\end{equation*}

### 2023-01-23 section4.tex
Commit serale

\subsection{From tropical polynomials to tLs}

@@

\begin{theorem}\label{thm:cont}
 Any tropical Laurent series $f:\Lawv^X\to\Lawv$ is continuous on $\BB R_{>0}^X$, w.r.t.\ to the norm $\norm{\cdot}_\infty$.
\end{theorem}
\begin{proof}
 It follows after adapting [Theorem , \cite{}] in order to prove that if a real-valued function on a locally convex topological $\BB R$-vector space is, locally around $x$, concave and bounded by a finite constant, then it is continuous at $x$.
\end{proof}

@@

\subsection{Lipschitz-continuity of tLs}%$\Lawv^{X}$ as a metric space.}

>>>>

\subsection{From tropical polynomials to tLs}\label{sec:4A}

@@

\begin{theorem}\label{thm:cont}
 Any tropical Laurent series $f:\Lawv^X\to\Lawv$ is continuous on $\BB R_{>0}^X$, w.r.t.\ to the norm $\norm{\cdot}_\infty$.
\end{theorem}
\begin{proof}
 It follows after adapting [Proposition 4.4, \cite{Cobzas2017}] in order to prove that if a real-valued function on a locally convex topological $\BB R$-vector space is, locally around $x$, concave and bounded by a finite constant, then it is continuous at $x$.
\end{proof}

@@

\subsection{Lipschitz-continuity of tLs}\label{sec:4C}%$\Lawv^{X}$ as a metric space.}
